Leadership across cultures and contexts

### 2019-10-08 leadership_across_cultures_contexts.Rmd
Added PCA work in analyses.
Working on introduction.

@@

Amont small-scale socities with relative egalitarianism and local political autonomy, coomunity leaders, in addition to being older, respected males, tend to be individuals with large social networks and strong social support. Physically, leaders across multople contexts tend to be taller and more physically formidable. Such physical embodiments might equip individuals for more eefective leadership in the context of inter-group conflicts as well as in the context of intra-group conflict resolution and in management of collective actions.

@@

The ability to shape group dynamics can provide enormous individual benefits to leaders, even if 'just for a while.'

@@

Using the same database of 1212 ethnographic paragraphs extracted from the 60-culture Probability Sample Files (PSF) of the electronic Human Relations Area Files (eHRAF) database. The leadershipdata was designed to capture a wide sample of the ethnographic record of leadership. Two authors coded each paragraph for presence of `r length(quality_vars)` distinct qualities of leaders, `r length(function_vars)` distinct functions leaders serve, and `r length(leader_benefit_vars)` benefits and `r length(leader_cost_vars)` costs that leader or followers may receive. Cost and benefits were operationalized prior to coding following our reading of the evolutionary leadership literature. See Table X. The operationalized qualities and functions (See Table X) were developed from the ethnographic text records in the database. First ZG read a subset of text records and developed initial variable lists and operationalizations of the qualities and functions in those text records. Then, KS coded all 1212 text records (in a random order) for the operationalized qualities, functions, cost, and benefits, **creating new variables and operationalizations for additional qualities and functions encountered**. After coding half of the random sample KS and ZG revised the operational definitions to produce the final list of variables in Tables XX. ZG then followed the same process of coding the entire sample of 1212 text records for the X operationalized variables. DISCUSS IRR. ZG and KS then discussed every instance of disagreement between their respective coding to produce a consensus matrix, which is used in the analyses here and added to the published data repository. For additional details on ethnographic sampling and creating of the leadershipdata package see CITE.

@@

@@

>>>>

The Global Leadership and Organizational Behavior Effectivensss (GLOBE) project is a large-scale international research program aimed at understanding leadership effectiveness and culturla variation across large organizations. The GLOBE project has produced multiple cross-national datasets on leadership and hundreds of publications. For example, *The GLOBE Study of CEO Leadership Behavior and Effectiveness in 24 Countries* draws on data from over 1,000 CEOs and over 5,000 senior executives from corporations in varied of industries across 24 countries. The goals of the GLOBE CEO Study were to address (1) how natioanl culture influences expectations for hte behaviors of leaders, (2) which behaviors of CEOs are typically associated with organizational success, (3) differences between high-functioning adn low-functionsing CEOs, adn (4) the importance of CEO behaviors aligning with societal expectations. Through path analysis the study concluded that culturla values indirectly predict CEO leadership behavior through culturally endorsed leadership expectations. That is, leaders moderate their behavior through culturally learned values and leadership-specific values.

The GLOBE CEO Study defines six "global leadership behaviors" developed from 21 "primary leadership beaviors." Among the global leadership behaviors, the GLOBE CEO STudy found that charimatic leadership beahvior is consistently the most important behavioral trait regarding firm performance and dedication of top managemnet team (TMT) members, followed by team-oriented behavior and human-oritented behavior. Participative leadership was moderately related to TMT dedication, however was not related to firm performance. The most successful CEOs are those who are rated as more visonary, performance oriented, and decisve. Furthermore, results strongly suggest the fit between a CEOs beahavioral profile and the expectations of leadership within a society strongly predict TMT dedication and firm performance.

@@

Among small-scale socities with relative egalitarianism and local political autonomy coomunity leaders, in addition to being older, respected males, tend to be individuals with large social networks and strong social support. Physically, leaders across multiple contexts tend to be taller and more physically formidable. Such physical embodiments might equip individuals for more eefective leadership in the context of inter-group conflicts as well as in the context of intra-group dispute settlement and in management of collective actions. Charisma and oratory skills are common properties of leaders, but are espeically important in the context of egalitarianism where individual leaders must rely on persuassion and more subtle forms of influence to convince community members to come to agreement.

The ability to shape group dynamics can provide enormous individual benefits to leaders, even if 'just for a while.' Fundamentally, leaders in any context are able to promote group policies which either align with their individual interests or which are not especially costly for themselves.

Across diverse populations and organizations, community leaders, political leaders, and organization leaders tend to have greater mating oppurtunities and therefore, given the aformentioned male-biase in top leadership positions, these leaders also tend to have greater reproductive success.

Instituionalized leadership positions are also typically associated with increased social status.

Leaders and high-status individuals are also more likely to be the recipeints of social support and material benefits in times of need.

@@

The unique costs associated with leadership positions have recieved less attention, relative to the benefits of leadership.

Group responsibilities necessarily impose oppurtunity costs on individual priorities and agendas.

In managing collective action and enacting group-level policies, some behaviors of leaders will upset some followers and leader-follower interactions can be hostile.

@@

Using the same database of 1212 ethnographic paragraphs (termed text-records) extracted from the 60-culture Probability Sample Files (PSF) of the electronic Human Relations Area Files (eHRAF) database. The leadershipdata was designed to capture a wide sample of the ethnographic record of leadership. Two authors coded each paragraph for presence of `r length(quality_vars)` distinct qualities of leaders, `r length(function_vars)` distinct functions leaders serve, and `r length(leader_benefit_vars)` benefits and `r length(leader_cost_vars)` costs that leader or followers may receive. Cost and benefits were operationalized prior to coding following our reading of the evolutionary leadership literature. See Table X. The operationalized qualities and functions (See Table X) were developed from the ethnographic text records in the database. First ZG read a subset of text records and developed initial variable lists and operationalizations of the qualities and functions in those text records. Then, KS coded all 1212 text records (in a random order) for the operationalized qualities, functions, cost, and benefits, **creating new variables and operationalizations for additional qualities and functions encountered**. After coding half of the random sample KS and ZG revised the operational definitions to produce the final list of variables in Tables XX. ZG then followed the same process of coding the entire sample of 1212 text records for the X operationalized variables. DISCUSS IRR. ZG and KS then discussed every instance of disagreement between their respective coding to produce a consensus matrix, which is used in the analyses here and added to the published data repository. For additional details on ethnographic sampling and creating of the leadershipdata package see CITE.

@@

We analyze data from our researcher-coded operationalized variables at the text record level and at the culture level. Our first goal was to assess the proportion of text records and cultures that provided evidence for each of our coded variables.

<!-- At the text record level, hierarchical cluster analysis was then used to identify natural groupings of all our coded variables. If variables from a model clustered together, and separately from the other variables, that would lend support to the theoretical cohesiveness of that model. If, on the other hand, variables from different models clustered together, that would suggest theoretical models may need revision or that clusters had identified components of a novel theoretical model.  -->

To reduce the dimensionality of the `r length(quality_vars)` quality variables and the

@@

The geographic distribution of the cultures in our sample is displayed in Fig. 1, with cultures labeled by mode of subsistence and represented by a symbol proportional to the number of documents that provide ethnographic texts for that culture (for details, see Table S1). The 1212 text records from `r length(unique(leadershipdata::documents$d_ID))` unique documents describing `r length(unique(leader_text2$d_culture))` cultures were generally short, with a median word count of X, a mean of X, and standard deviation of X. The vast majority of text records pertained to male leadership (89.8%, 898 text records) and very few pertained to female leadership (2.5%, 25 text records).In7 instances (0.7%)textrecordspertain tobothmales and females,and in69 text records (6.9%) sex was unknown.

NEED TO DISCUSS 1187 and split records.

## Variable distributions

For each of the X coded variables, we computed the percentage of text records that provided support, estimating standard errors using a binomial generalized linear mixed effects model with a random intercept for author nested within culture. See FIG.

```{r, echo=FALSE, warning=FALSE, message=F, fig.width=15, fig.height=8}
plot.variable.support
```

Costs and benefits.

```{r, echo=FALSE, warning=FALSE, message=F, fig.width=15, fig.height=8}
plot.variable.support_costs_benefits
```
